An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-04-01 tex/paper.tex
Adding a reuse section

The names of all the contributors are not known: as these were mainly done
through github and certain have not provided their name or responded to a
request for further details. Here is an incomplete list:

@@

\subsection{Archive}
\subsection{Code repository}

@@

>>>>

The names of all the contributors are not known: as these were mainly done
through Github and certain have not provided their name or responded to a
request for further details. Here is an incomplete list:

@@

\subsection{Archive}

\begin{multicols}{2}
    \begin{itemize}
        \item Name: Zenodo
        \item Persistent identifier:
\href{https://zenodo.org/record/45187}{10.5281/zenodo.45187}
        \item Licence: MIT
        \item Publisher:  Vincent Knight
        \item Version published: Axelrod: Alternator Release. v0.0.28
        \item Date published: 2016-01-26
    \end{itemize}
\end{multicols}

\subsection{Code repository}

\begin{multicols}{2}
    \begin{itemize}
        \item Name: Github
        \item Identifier: \url{https://github.com/Axelrod-Python/Axelrod}
        \item Licence: MIT
        \item Date published: 2015-02-16
    \end{itemize}
\end{multicols}

@@

The Axelrod library has been designed with sustainable software practice in
mind. There is an extensive documentation suite:
\url{axelrod.readthedocs.org/en/latest/}. Furthermore, there is a growing set
of example Jupyter notebooks available here:
\url{https://github.com/Axelrod-Python/Axelrod-notebooks}.

This library has the potential to be a common standard for research in to the
iterated Prisoner's dilemma. In particular, having a large library of
tested strategies readily available for experimentation is of high value to the
research community.

This has been evidenced by the work described in
Section~\ref{sec:new-strategies-and-implications} the library has already shown
it's potential for reuse.
